Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 2 is ready and in the document.

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") -> b

@@

@@

```{r fig.width=10, fig.height=5}

>>>>

```{r fig.width=6, fig.height=5}

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw(base_size = 7) +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw(base_size = 7) +
  theme(legend.position = "right") -> b

@@

GP_mles %>% 
    mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
  theme_bw(base_size = 7) +
  theme(legend.position = "none") -> c

abplot <- plot_grid(a, b + theme(legend.position = "none"), c, nrow = 3)

plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
ggsave("Ch3_samplesize/Figures/Figure2.png")

@@

```{r eval=FALSE, fig.width=10, fig.height=5}
